Title

### 2023-03-14 Quarto Template.qmd
Update Quarto Template.qmd

---
title: "Title"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: visual
---

@@

# figure

>>>>

---
title: "Title"
author: "Tim Vigers"
date: "today"
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
editor: source
---

@@

# Figure
